### 2014-06-06 paper/body.tex
selffer --> selfer

\begin{itemize}
\item A \emph{selffer} network \net{B3B} where the first $3$ layers are copied from \net{baseB} and frozen. The five higher layers are initialized randomly and trained toward dataset \dB. Here we're only using data from \dB and layers from a network \net{baseB}, that was trained on \dB. This may seem a little strange, but we actually need it as an additional control for the below transfer network.

@@

\begin{itemize}
\item A \emph{selffer} network \net{B3B^+} just like \net{B3B}, but where all layers learn
\item A \emph{transfer} network \net{A3B^+} just like \net{A3B}, but where all layers learn
\end{itemize}

@@

\begin{figure}[htpb]
\begin{center}
\includegraphics[width=1\linewidth]{plots/result_transfer_crop.pdf}
\includegraphics[width=1\linewidth]{plots/result_transfer_lines_crop.pdf}
\end{center}
\caption{Accuracy of each treatment and control. \emph{Top panel:} Raw data. \emph{Bottom panel}: Lines connect the medians of each treatment. Shaded areas and text highlight key takeaway messages. \todo{This is the min. required if we explain the figure in the main text.}
}
\label{fig:results}
\end{figure}

@@

\begin{table}[t]
\caption{Performance accuracy boost of transfer + fine-tuning \net{BnA^+} over controls. All differences are significant at the $p < .001$ level.}
\label{tab:boost}
\begin{center}
\begin{tabular}{|c|c|c|}
\hline
           & mean boost  & mean boost \\
layers     & over        & over \\
aggregated & \net{baseA} & selffer \net{AnA^+} \\
\hline
1-7        & 1.6\%       & 1.4\% \\
3-7        & 1.8\%       & 1.4\% \\
5-7        & 2.1\%       & 1.7\% \\
\hline
\end{tabular}
\end{center}
\end{table}

>>>>

\begin{itemize}
\item A \emph{selfer} network \net{B3B} where the first $3$ layers are copied from \net{baseB} and frozen. The five higher layers are initialized randomly and trained toward dataset \dB. Here we're only using data from \dB and layers from a network \net{baseB}, that was trained on \dB. This may seem a little strange, but we actually need it as an additional control for the below transfer network.

@@

\begin{itemize}
\item A \emph{selfer} network \net{B3B^+} just like \net{B3B}, but where all layers learn
\item A \emph{transfer} network \net{A3B^+} just like \net{A3B}, but where all layers learn
\end{itemize}

@@

\begin{figure}[htpb]
\begin{center}
\includegraphics[width=1\linewidth]{plots/result_transfer_crop.pdf}
\includegraphics[width=1\linewidth]{plots/result_transfer_lines_crop.pdf}
\end{center}
\caption{Accuracy of each treatment and control. \emph{Top panel:} Raw data. \emph{Bottom panel}: Lines connect the medians of each treatment. Shaded areas and text highlight key takeaway messages. \todo{This is the min. required if we explain the figure in the main text.}
\todo{Here and in all figs, remove one f from selfer}
}
\label{fig:results}
\end{figure}

@@

\begin{table}[t]
\caption{Performance accuracy boost of transfer + fine-tuning \net{BnA^+} over controls. All differences are significant at the $p < .001$ level.}
\label{tab:boost}
\begin{center}
\begin{tabular}{|c|c|c|}
\hline
           & mean boost  & mean boost \\
layers     & over        & over \\
aggregated & \net{baseA} & selfer \net{AnA^+} \\
\hline
1-7        & 1.6\%       & 1.4\% \\
3-7        & 1.8\%       & 1.4\% \\
5-7        & 2.1\%       & 1.7\% \\
\hline
\end{tabular}
\end{center}
\end{table}
